%\subsection{Experiment Execution}
%    \label{subsec:Experiment_execution}
%    %%Task description, stage 1 to 3 with survey
%    \input{Text/MethodExperimentExecution}
%!text

The experiment assesses participants' reactions to complex facade variations in VR, using CICA-derived complexity data (element 3.2 in Figure~\ref{fig:Experiment_and_Data_Analysis_flowchart}) and gathers their impression regarding evaluating facade complexity.
\added{
The participant pool consisted of 26 individuals, comprising 13 males and 13 females, aged between 18 and 31. A majority were university students, with varied backgrounds including construction and facade design. These demographic factors are revisited in the discussion and limitations sections to assess generalizability.
}

\deleted{It consists of three stages:}

\added{
The experiment consists of three stages:
}
%!VR interaction stage
\begin{enumerate}
    \item \textit{`VR interaction' stage:}  as illustrated in the flowchart in Figure~\ref{fig:Experiment_and_Data_Analysis_flowchart}~(element I) \deleted{Figure 4 (element 3.2 I)}, participants engage with a VR simulation of the actual laboratory and building where the experiment takes place \deleted{(Figure 7)} (see Figure~\ref{fig:CICA_and_VR_flowchart}, element 3).~They select preferred facade variations from three patterns, each with ten complexity-labeled variations \deleted{(Figure~\ref{fig:modeling_flowchart})} and data visualization of their CICA complexity score, considering the scenario as their permanent workplace or study location.
    Patterns' variations are presented in randomized order to ensure unbiased results, accessible through the VR interface.

    \item \textit{`Screen-based Ranking' Stage:} As depicted in the flowchart in Figure~\ref{fig:Experiment_and_Data_Analysis_flowchart}~(element II) \deleted{Figure 4 (element 3.2 II)}, participants rank the same 10 facade variations based on their perception of complexity via a screen-based interface without CICA system data.
    This is conducted for each of the three patterns to refine the CICA system's complexity analysis capabilities.

    \item \textit{`Post-interaction' Survey:} As shown in the flowchart in Figure~\ref{fig:Experiment_and_Data_Analysis_flowchart}~(element III)\deleted{Figure 4 (element 3.2 III)}, after completing the first two stages, participants answer a 15-question survey divided into Participant Background (Figures~\ref{fig:SurveyBackgroundChart}~\ref{fig:SurveyYearsExperienceChart}) and Complexity Perception sections(Figures~\ref{fig:SurveyQuestions6-10}~\ref{fig:SurveyQuestions11-15}), exploring qualitative perceptions of complexity and the factors influencing their choices.
    This section uses a 7-point Likert scale for capturing detailed responses.
\end{enumerate}

%! Metrics purpose
\deleted{
The combined analysis of these stages aims to provide insights into user tolerance for complex facades and its implications for future construction trends.
By merging quantitative and qualitative findings, we contribute to the discourse on architectural complexity and its impact on contemporary design and construction.}

\added{
The combined analysis of these stages provides a comprehensive understanding of how users engage with and perceive facade complexity. By merging quantitative and qualitative findings, we contribute to the discourse on architectural complexity and its impact on contemporary design and construction.
}
