%\subsection{Experiment design}
%    \label{subsection:Experiment_design}
%    %%Task description, stage 1 to 3 with survey
%    \input{Text/ExperimentDesign}

%!text

The experiment is designed to assess participants' reactions to increasingly complex facade variations in VR simulations, using the CICA system-derived complexity data (element 3.2 in Figure~\ref{fig:MethodologyFlowchart}). It unfolds across three stages:

%!VR interaction stage
\begin{enumerate}
    \item \textit{`VR interaction' stage:}  as illustrated in the flowchart in Figure~\ref{fig:MethodologyFlowchart}~(element 3.2 I), participants were introduced to a VR simulation replicating the actual laboratory and building where the experiment took place (Figure~\ref{fig:VRinterface}).
    Their task was to select preferred facade variation from three patterns, each with ten complexity-labeled variations (Table~\ref{tab:PatternsVariationsPart0}) alongside data visualization of their CICA complexity score, considering the scenario where the laboratory would be their permanent workplace or study location.
    The patterns were presented in randomized order to ensure unbiased results and were accessible through the VR interface.
    The stage aims to gauge participants' complexity tolerance levels.
    \item \textit{`Screen-based Ranking' Stage:} As depicted in the flowchart in Figure~\ref{fig:MethodologyFlowchart}~(element 3.2 II), participants rank the same 10 facade variations based on their perception of complexity, through a screen-based interface, without CICA system data.
    This process was conducted for each of the three patterns.
    The aim of this analysis was to refine the CICA system's complexity analysis capabilities, thereby enhancing the accuracy of future architectural trend forecasts.
    \item \textit{`Post-interaction' Survey:} As shown in the flowchart in Figure~\ref{fig:MethodologyFlowchart}~(element 3.2 III), following the completion of the first two stages, participants answer a 15-question survey divided into Participant Background (Figures~\ref{fig:SurveyBackgroundChart}~\ref{fig:SurveyYearsExperienceChart}) and Complexity Perception sections (Figures~\ref{fig:SurveyQuestions6-10}~\ref{fig:SurveyQuestions11-15}) exploring participants' qualitative perceptions of complexity and the factors influencing their facade variation choices.
    This final section uses a 7-point Likert scale, chosen for its effectiveness in capturing detailed responses regarding complexity perception and element arrangement in facade design.
\end{enumerate}

%! Metrics purpose

The combined analysis of these stages aims to provide insights into user tolerance for complex facades and its implications for future construction trends.
By merging quantitative and qualitative findings, we contribute to the discourse on architectural complexity and its impact on contemporary design and construction.