%\subsection{Data Analysis and Validation}
%    \label{subsec:Data_analysis}
%    \input{text/Method_DataAnalysis}

The final phase of our methodology focuses on analyzing the data collected during the experiments and the application of the CICA system to images of historical buildings, aiming to validate the effectiveness of the `Complexity Analysis' system in quantifying facade complexity and aligning it with user perceptions (see Figure~\ref{fig:Experiment_and_Data_Analysis_flowchart}, element 3.3).

\textit{Data Processing and Analysis:} We assess CICA scores from historical buildings to identify patterns across different architectural styles and analyze experiment data using statistical tools to understand perceptions of complexity.

\textit{Performance Evaluation:} The efficacy of the `Complexity Analysis' system and the CICA score is assessed through:
\begin{itemize}
    \item \textit{Accuracy Analysis:} Evaluating the alignment between CICA scores and user perceptions.
    \item \textit{Participant Perception:} Analyzing user feedback to gain insights into the impact of complex facades.
\end{itemize}

\textit{Results Interpretation and Reporting:} Synthesizing data to confirm the validity of the CICA system and its applicability in architectural design.

While the primary focus of this phase is on validating the CICA system’s ability to quantify complexity, the combined analysis of historical architectural trends and real-time user perceptions provides potential insights into future construction trends.
By comparing these historical trends with user preferences gathered in the VR experiment, the CICA system provides a framework for predicting future design shifts.
Additionally, through the system’s ability to conduct accuracy analysis, architects could better identify the optimal range of complexity that appeals to users, allowing for the design of facades that align with predicted trends while balancing aesthetic interest and functional sustainability.
Over time, as more data is gathered, the CICA system's predictive capabilities could offer architects valuable foresight into emerging trends in facade design that might become prominent in future construction practices.

This structured approach ensures a thorough evaluation, providing insights into the relationship between facade complexity and user perception.







