%!\section{Results}
%\label{sec:Results}
%\input{text/ResultsIntro.tex}

%=============================
%%% Results should be clear and concise.
%Report the results of the study
%Report main findings concisely in a logical order

%===============

In this section, we embark on a journey through the outcomes of our extensive study.
Our research was designed to delve into the intricate world of architectural complexity, investigating how users perceive and respond to increasing levels of complexity in facade design.
Our primary aim was to measure their tolerance for intricate facade designs, with the ultimate goal of contributing valuable insights to the ongoing discourse on future construction trends.

Building upon the methodologies outlined in the previous section, we present our findings in a structured manner.
The results are divided into two distinct sections: firstly, the outcomes of our `Computational Image Complexity Analysis' (CICA) application across different epochs and architectural styles (see Figure \ref{fig:HistoricalComplexityGraph}), and secondly, the results derived from our experiment gauging user responses to complex facades.

However, it's essential to recognize that every research endeavor carries its unique set of limitations, and our study is no exception.
In the spirit of transparency, we candidly acknowledge these limitations, which we will address.
Nevertheless, the following subsections, which meticulously analyze our results, were arranged in accordance with the core themes and research questions that guided our inquiry.



